Multi-output Bus Travel Time Prediction\\ Using Convolutional LSTM Neural Network

### 2017-11-02 paper/paper.tex
Wörk, wörk, wörk.

\begin{figure*}[!t]
    \centering
    \begin{subfigure}[t]{0.31\textwidth}
        \centering
        \includegraphics[width=\textwidth]{plots/decycle_5min.pdf}
        \caption{5 min}
    \end{subfigure}%
    ~ 
    \begin{subfigure}[t]{0.31\textwidth}
        \centering
        \includegraphics[width=\textwidth]{plots/decycle_15min.pdf}
        \caption{15 min}
    \end{subfigure}
    ~
    \begin{subfigure}[t]{0.31\textwidth}
        \centering
        \includegraphics[width=\textwidth]{plots/decycle_30min.pdf}
        \caption{30 min}
    \end{subfigure}

@@

\subsection{Data preprocessing}
Furthermore, to allow predictions for fixed time-steps ahead, data was aggregated at a fixed resolution. \Cref{fig:resolutions} shows examples of travel time for a single link and a single day at various time resolutions. The red dots are actual measurements, and the blue line the aggregated resolution. The choice depends of the \emph{expected} frequency of the line, and is a balance between capturing the details and still having a reasonal number of measurements in each time-step.

>>>>

\begin{figure*}[!t]
    \centering
    \begin{subfigure}[t]{0.31\textwidth}
        \centering
        \includegraphics[width=\textwidth]{plots/decycle_5min_n.pdf}
        \caption{5 min}
    \end{subfigure}%
    ~ 
    \begin{subfigure}[t]{0.31\textwidth}
        \centering
        \includegraphics[width=\textwidth]{plots/decycle_15min_n.pdf}
        \caption{15 min}
    \end{subfigure}
    ~
    \begin{subfigure}[t]{0.31\textwidth}
        \centering
        \includegraphics[width=\textwidth]{plots/decycle_30min_n.pdf}
        \caption{30 min}
    \end{subfigure}

@@

\subsection{Time resolution}
To allow predictions for fixed time-steps ahead, data is aggregated at a fixed resolution. \Cref{fig:resolutions} shows examples of travel time for a single link and a single day at various time resolutions. The black dots are actual measurements, and the lines the aggregated link travel time at the given resolution. The choice depends of the \emph{expected} frequency of the line, and is a balance between capturing the details and still having a reasonal number of measurements in each time-step.
